Space-time adaptivity for parabolic evolution equations

### 2020-05-26 Latex/paper.tex
current status

\usepackage{amsaddr}
\usepackage{babel}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{commath}
\usepackage{colortbl}
\usepackage{dsfont}
\usepackage{enumerate}
\usepackage{esint}
\usepackage[left=0.09\paperwidth, right=0.15\paperwidth, bottom=0.12\paperheight]{geometry}
\usepackage{graphicx}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow,bigdelim}
\usepackage{url}
\usepackage{pdflscape}
\usepackage{rotating}
%\usepackage[outer]{showlabels}
\usepackage[color=white,linecolor=black, textwidth=0.12\paperwidth]{todonotes}
%\setlength{\parindent}{0pt}
\usepackage{wrapfig}

@@

\usepackage{color}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\providecommand\C{}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\K}{\mathcal{K}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\bbD}{\mathbb{D}}
\newcommand{\f}{\varphi}
\newcommand{\e}{\varepsilon}
\newcommand{\eps}{\varepsilon}
\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\newcommand{\z}{\zeta}
\renewcommand{\O}{\Omega}
\renewcommand{\P}{\mathbb P}
\newcommand{\intRn}{\int_{\R^n}}
\newcommand{\sumi}{\sum_{i=1}^n}
\newcommand{\sumij}{\sum_{i,j=1}^n}
\renewcommand{\d}{\delta}
\newcommand{\p}{\partial}
\DeclareMathOperator{\osc}{osc}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\gen}{gen}
\DeclareMathOperator{\cat}{Cat}
\DeclareMathOperator{\Cat}{Cat}
\DeclareMathOperator{\Div}{div}
\DeclareMathOperator{\blockdiag}{blockdiag}
\renewcommand{\div}{\Div}
\providecommand{\spann}{\mathrm{span}}
\providecommand{\diam}{\mathrm{diam}}
\providecommand{\dist}{\mathrm{dist}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\usepackage{stmaryrd}
\newcommand{\jump}[1]{\left\llbracket #1 \right\rrbracket}
\newcommand{\rhu}{\rightharpoonup}
\newcommand{\T}{\mathcal{T}}
\newcommand{\V}{\mathcal{V}}
\DeclareMathOperator*{\dof}{\#\!DoF}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\Id}{Id}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\providecommand\note{}
\newcommand{\new}[1]{{\color{ao(english)} #1}}
\renewcommand{\L}{\mathcal L}
\newcommand{\Y}{\mathcal Y}
\newcommand{\Lto}{{L_2(\Omega)}}
\newcommand{\bbT}{\mathbb{T}}
\newcommand{\cL}{\mathcal L}
\newcommand{\Lis}{\cL\mathrm{is}}
\newcommand{\udelta}{{\underline{\delta}}}
\newcommand{\jw}[1]{{\color{red}{JW: #1}}}
\newcommand{\rvv}[1]{{\color{teal}{RvV: #1}}}
\DeclareMathOperator*{\ran}{ran}

@@

Let $T \in (0, \infty)$ be given, and set $I := (0, T)$. We make the following assumption.
\begin{assum}
  \label{assum:a}
  For a.e. $t$, let $a(t;\cdot,\cdot)$ denote a bilinear form on $V \times V$ that is
  \begin{alignat*}{3}
    t \mapsto a(t; \eta, \zeta) & ~~ \text{is measurable} \quad && (\eta, \zeta \in V) \\
    |a(t;\eta,\zeta)| & \lesssim  \|\eta\|_{V} \|\zeta\|_{V} &&(\eta,\zeta \in V) &&\text{(bounded)}, \\
     a(t;\eta,\eta)   & \gtrsim   \|\eta\|_{V}^2 &&(\eta \in {V}) &&\text{(coercive)}.
  \end{alignat*}
\end{assum}

@@

\subsection{Andreev formulation}
Defining $A, A_s \in \Lis(Y,Y')$, $A_a \in \cL(Y,Y')$, and $\partial_t \in \cL(X,Y')$ by 
\[
(Au)(v):=\int_I a(t;u(t),v(t)) \dif t, \quad A_s:=\tfrac12(A+A'), \quad A_a:=\tfrac12(A-A'), \quad \partial_t:=B-A,
\]
an equivalent self-adjoint saddle point formulation of \eqref{eqn:B-varform} was
introduced by Andreev in \cite{Andreev2013} as finding the solution $(\mu,u) \in Y\times X$ of
\[
  \begin{bmatrix} A_s & B\\ B' & -\gamma_0' \gamma_0 \end{bmatrix}
  \begin{bmatrix} \mu \\ u \end{bmatrix}=
  \begin{bmatrix} g \\ -\gamma_0' u_0 \end{bmatrix}.
\]
Thanks to \eqref{eqn:B-lis}, the Schur complement $S := B' A_s^{-1} B+\gamma_0'\gamma_0$ is in $\Lis(X, X')$, is self-adjoint, and coercive.

@@

Let $(X^\delta)_{\delta \in \Delta}$ be a collection of closed subspaces of $X$. 
We define a \emph{partial order} on $\Delta$ by $\delta \preceq \tilde{\delta}$
when $X^\delta \subseteq X^{\tilde{\delta}}$. For $\delta \in \Delta$, let
$u_\delta \in X^\delta$ denote the {\em Galerkin approximation to $u$}, i.e., the solution of
\begin{equation}
(Su_\delta)(v)=f(v) \quad (v \in X^\delta), 
  \label{eqn:galerkin}
\end{equation}
being the best approximation to $u$ from $X^\delta$ w.r.t.~$\|\cdot\|_X$.

\subsection{Discretized problem}
Applying $S$ requires the application of the nonlocal operator $A_s^{-1}$, making it
unsuitable for practical computation. To that end, let $(Y^\delta)_{\delta \in \Delta}$
be a collection of closed subspaces of $Y$ satisfying $X^\delta \subseteq Y^\delta$
that is \emph{uniformly inf-sup stable}, i.e.
\begin{equation}
  \gamma_\Delta:=\inf_{\delta \in \Delta}\inf_{0 \neq w \in X^\delta}\sup_{0\neq y^\delta \in Y^\delta} \frac{(\partial_t w)(v)}{\|\partial_t w\|_{Y'}\|v\|_Y} \in (0,1].
  \label{eqn:infinfsup}
\end{equation}
Uniform stability essentially establishes the norm equivalences
\[
  \gamma_\Delta ||\partial_t w||_{Y'} \leq ||\partial_t w||_{{Y^\delta}'} \leq ||\partial_t w||_{Y'} \quad (w \in Y, \delta \in \Delta).
\]
Note that $\gamma_\Delta$ can be made arbitrarily close to $1$ by selecting $Y^\delta$ sufficiently large.

For $\delta, \hat{\delta} \in \Delta$ with $Y^{\hat{\delta}} \supseteq Y^\delta$, and 
$E_Y^{\hat{\delta}}$, $E_X^\delta$ denoting the embeddings $Y^{\hat{\delta}} \rightarrow Y$,
$X^\delta \rightarrow X$, let $(\mu^{\hat{\delta} \delta},u^{\hat{\delta} \delta}) \in Y^{\hat{\delta}} \times X^\delta$ be the solution of 
\[
  \begin{bmatrix}{E_Y^{\hat{\delta}}}' A_s E_Y^{\hat{\delta}}& {E_Y^{\hat{\delta}}}' B E^\delta_X\\ {E^\delta_X}' B' E_Y^{\hat{\delta}}& -{E^\delta_X}' \gamma_0' \gamma_0 E^\delta_X \end{bmatrix}
  \begin{bmatrix} \mu^{\hat{\delta} \delta} \\ u^{\hat{\delta} \delta} \end{bmatrix}
  \begin{bmatrix} {E^{\hat{\delta}}_Y}' g \\ -{E^\delta_X}' \gamma_0' u_0 \end{bmatrix}
\]
or
\begin{equation}
  \label{eqn:discr-schur}
  \underbrace{
    {E^\delta_X}'(B' E^{\hat{\delta}}_Y({E^{\hat{\delta}}_Y}' A_s E^{\hat{\delta}}_Y)^{-1} {E^{\hat{\delta}}_Y}' B +\gamma_0'\gamma_0)E^\delta_X
  }_{S^{\hat{\delta} \delta}:=}u^{\hat{\delta} \delta}
  =
  \underbrace{
    {E^\delta_X}' (B' E^{\hat{\delta}}_Y({E^{\hat{\delta}}_Y}' A_s E^{\hat{\delta}}_Y)^{-1} {E^{\hat{\delta}}_Y}' g+\gamma_0' u_0)
  }_{f^{\hat{\delta} \delta}:=}.
\end{equation}\rvv{heavy notatie uitstellen?}
Unless $Y^{\hat{\delta}}=Y$, it holds that $S^{\hat{\delta} \delta} \neq {E_X^\delta}' S E_X^\delta$ and $f^{\hat{\delta} \delta} \neq {E_X^\delta}'f$, and so generally $u^{\hat{\delta} \delta} \neq u_\delta$.

Equipping $X^\delta$ with `energy' norm $\|w\|^2_{X^{\hat{\delta}\delta}}:=\|w\|^2_{Y}+ \|\partial_t w\|_{{Y^\delta}'}+\|\gamma_T w\|^2$,
from \cite[Lemma~3.3]{Stevenson2020a} it follows that
$\|\cdot\|_{X^{\hat{\delta}\delta}}^2=(S^{\hat{\delta}\delta}\cdot)(\cdot)$,
similar to Lemma~\ref{lem:energy-norm}. As shown in \cite[Thm.~3.6]{Stevenson2020a}, we have
\begin{equation}
  \label{eqn:galerkin-ortho}
  \|u-u^{\hat{\delta}\delta}\|_X \leq \gamma_\Delta^{-1} \|u-u_\delta\|_X,
\end{equation}
whereas by definition of $\gamma_\Delta$ it holds that
\begin{equation}
  \label{eqn:X-norm-equiv}
  \gamma_\Delta\|\cdot\|_{X} \leq \|\cdot\|_{X^{\hat{\delta}\delta}} \leq \|\cdot\|_{X} \quad\text{on } X^\delta.
\end{equation}

@@

\subsection{The spatial meshes}
The following result generalizes \cite[Lemma 6.2]{11} and \cite[Proposition 2.5]{258.4}
by allowing $W \neq \tilde W$.

@@

\subsection{Wavelets in time, finite elements in space}
Let ${\mathcal O}$ be a collection of pairs of closed subspaces $(W,\tilde{W})$
as in Proposition~\ref{prop:space-infsup} with uniform inf-sup constant $\gamma>0$.

@@

We will assume that $\Sigma$ and $\Psi$ are locally supported, which in particular
means that $|\supp \sigma_\lambda| \lesssim 2^{-|\lambda|}$ and
$|\supp \psi_\lambda| \lesssim 2^{-|\lambda|}$. Furthermore, to ensure an
efficient stiffness matrix evaluation, we will shirtly impose a \emph{doubletree constraint}
on $X^\delta$ and $Y^\delta$, which will have the consequence that for any
$\lambda \in \vee_\Sigma$ with $\tilde{W}_\lambda^\delta \neq \{0\}$, and any
$\ell <|\lambda|$, there exists a $\mu \in \vee_\Sigma$ with $|\mu|=\ell$
($\mu$ being the `ancestor' of $\lambda$) with
$\dist(\supp \sigma_\mu,\supp \sigma_\lambda)\lesssim 2^{-|\mu|}$ and
$\tilde{W}_\mu^\delta \supset \tilde{W}_\lambda^\delta$.
We infer that \eqref{eqn:Y-space-refined} and thus \eqref{eqn:pre-doubletree} can
be ensured for $Y^\delta$ with $\dim Y^\delta \lesssim \dim X^\delta$.

In particular, for $\lambda \in \vee_\Psi$, let $S(\lambda)$ be the neighborhood
of $\supp \psi_\lambda$ with $\diam S(\lambda) \lesssim 2^{-|\lambda|}$ s.t.~$S(\lambda) \subset S(\mu)$
whenever $\lambda$ is a child of $\mu \in \vee_\Psi$. Then, assuming the doubletree
constraint on $X^\delta$, \eqref{eqn:Y-space-refined} is ensured under the condition
that
\[
  |\mu| = |\lambda| \wedge|\supp \psi_\mu \cap \supp S(\lambda)|>0 \implies \tilde{V}^\delta_\mu \supset  \tilde{W}^\delta_\lambda.
\]
\jw{Dit is min-of-meer copy-paste uit followup maar ik vind het nu nog wel cryptisch :-(}

\begin{example}
  Consider pairs $(W, \tilde W) \in \mathcal O$ where $W = \tilde W$.
  Let any $\sigma_\lambda$ be a continuous piecewise polynomial of degree $d-1$\jw{voor $d$ de dimensie van je space domain?! of gewoon *een* $d$? in het tweede geval: rename naar $p$?}
  w.r.t.~a uniform partition of $I$ into $2^{|\lambda|}$ subintervals, and let 
  $\Psi=\tilde{\Psi}$ be such that $\spann\{\tilde{\psi}_\lambda : |\mu| \leq |\lambda|\}$
  includes all piecewise polynomials of degree $d-2$ w.r.t.~a uniform partition
  of $I$ into $2^{|\lambda|}$ subintervals so that \eqref{eqn:deriv-orthogonal}
  is satisfied. If $\spann\{\tilde{\psi}_\lambda : |\mu| \leq |\lambda|\}$ even
  includes all piecewise polynomials of degree $d-1$ w.r.t.~a uniform partition
  of $I$ into $2^{|\lambda|}$ subintervals, then $Y^\delta$ as constructed above
  additionally satisfies
  \begin{equation}
    \label{eqn:inclusion}
      \framebox{$X^\delta \subset Y^\delta$}.
  \end{equation}
\end{example}

\begin{example}
  \label{ex:wavelets}
  \jw{dit moet misschien niet een voorbeeld zijn maar een eigen subsectie}
  Consider linear temporal wavelets and linear spatial finite element spaces.
  For $\Sigma$, we take the continuous 3-point from Figure~\ref{fig:3pt-wavelet}
  \jw{waarom is dit een Riesz basis? dit heeft een citatie nodig met wat meer info, bv \cite{Stevenson1998}?}.
  For this basis, $S(\lambda) = \supp \sigma_\lambda$.
  \begin{figure}
    \caption{3-point wavelet.}
    \label{fig:3pt-wavelet}
  \end{figure}

  For $\Psi$, we take the discontinuous orthogonal piecewise linear wavelet basis
  of Figure~\ref{fig:ortho-wavelet}\jw{again, needs citation; ik kon niks vinden zo 1-2-3;
  misschien omdat het niet echt een ``wavelet'' in de typische zin is?} For this
  basis, again $S(\lambda) = \supp \psi_\lambda)$.
  \begin{figure}
    \caption{orthogonal wavelet.}
    \label{fig:ortho-wavelet}
  \end{figure}

  In the spatial axis, we consider the collection $\mathbb T$ of conforming
  triangulations generated by NVB from some coarsest triangulation $\T_\perp$,
  and define $V_\T = V_\T$ the space of continuous piecewise linears w.r.t.~$\T$
  that vanish on $\partial \Omega$ such that $X^\delta := \sum_{\lambda \in \vee^\delta_\Sigma} \sigma_\lambda \otimes V_{\T_{\vee^\delta_\Sigma, \lambda}}$ satisfies the doubletree constraint.
  This means that when $\mu \in \vee^\delta_\Sigma$ is a parent of $\lambda \in \vee^\delta_\Sigma$,
      then $\T_{\vee^\delta_\Sigma, \mu}$ is a refinement of $\T_{\vee^\delta_\Sigma, \lambda}$, and that $\vee^\delta_\Sigma$ is a subtree of $\vee_\Sigma$, meaning
  \begin{itemize}
    \item it contains all wavelets on level 0, and
    \item if it contains a wavelet of level $\lambda \geq 1$, then it also contains
      its parents.
  \end{itemize}
\end{example}

\begin{remark}
When equipping the finite element spaces $V_{\T}$ with the hierarchical basis,
this doubletree constraint coincides with the constraint on the index set of
the basis for $X^\delta$; see e.g.~\cite{TODO}.
\end{remark}

We consider spaces $Y^\delta = \tilde Y^\delta$ of the form
$Y^\delta := \sum_{\lambda \in \vee^\delta_\Psi} \psi_\lambda \otimes V_{\T_{\vee^\delta_\Psi, \lambda}}$
for $\T_{\vee^\delta_\Psi, \lambda} \in \mathbb T$, again satisfying the doubletree
constraint. The choice
\[
  Y^\delta = \sum_{\lambda \in \vee_\Sigma^\delta} \sum_{\{\mu \in \vee_\Psi\colon |\mu|=|\lambda|,\,
|\supp \sigma_\lambda \cap \supp \psi_\mu|>0\}} \psi_\mu \otimes V_{\T_{\vee_\Sigma^\delta,\lambda}}
\]
is a doubletree by virtue of $X^\delta$ being one, and for this pair $(X^\delta, Y^\delta)$, \eqref{eqn:d_tX-in-Y} and \eqref{eqn:inclusion} are valid.

>>>>

\usepackage{showlabels}
\usepackage[boxed]{algorithm2e}
\usepackage{amsaddr}
\usepackage{babel}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{commath}
\usepackage{colortbl}
\usepackage{dsfont}
\usepackage{enumerate}
\usepackage{esint}
\usepackage[left=0.09\paperwidth, right=0.15\paperwidth, bottom=0.12\paperheight]{geometry}
\usepackage{graphicx}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow,bigdelim}
\usepackage{url}
\usepackage{pdflscape}
\usepackage{rotating}
%\usepackage[outer]{showlabels}
\usepackage[color=white,linecolor=black, textwidth=0.12\paperwidth]{todonotes}
%\setlength{\parindent}{0pt}
\usepackage{wrapfig}

@@

\usepackage{color}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\providecommand\C{}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\K}{\mathcal{K}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\bbD}{\mathbb{D}}
\newcommand{\f}{\varphi}
\newcommand{\e}{\varepsilon}
\newcommand{\eps}{\varepsilon}
\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\newcommand{\z}{\zeta}
\renewcommand{\O}{\Omega}
\renewcommand{\P}{\mathbb P}
\newcommand{\intRn}{\int_{\R^n}}
\newcommand{\sumi}{\sum_{i=1}^n}
\newcommand{\sumij}{\sum_{i,j=1}^n}
\renewcommand{\d}{\delta}
\newcommand{\p}{\partial}
\DeclareMathOperator{\osc}{osc}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\gen}{gen}
\DeclareMathOperator{\cat}{Cat}
\DeclareMathOperator{\Cat}{Cat}
\DeclareMathOperator{\Div}{div}
\DeclareMathOperator{\blockdiag}{blockdiag}
\renewcommand{\div}{\Div}
\DeclareMathOperator{\spann}{span}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\dist}{dist}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\usepackage{stmaryrd}
\newcommand{\jump}[1]{\left\llbracket #1 \right\rrbracket}
\newcommand{\rhu}{\rightharpoonup}
\newcommand{\T}{\mathcal{T}}
\newcommand{\V}{\mathcal{V}}
\DeclareMathOperator*{\dof}{\#\!DoF}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\Id}{Id}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\providecommand\note{}
\newcommand{\new}[1]{{\color{ao(english)} #1}}
\renewcommand{\L}{\mathcal L}
\newcommand{\Y}{\mathcal Y}
\newcommand{\Lto}{{L_2(\Omega)}}
\newcommand{\bbT}{\mathbb{T}}
\newcommand{\cL}{\mathcal L}
\newcommand{\Lis}{\cL\mathrm{is}}
\newcommand{\udelta}{{\underline{\delta}}}
\newcommand{\jw}[1]{{\color{red}{JW: #1}}}
\newcommand{\rvv}[1]{{\color{teal}{RvV: #1}}}
\DeclareMathOperator*{\ran}{ran}
\SetKwRepeat{Do}{do}{while}%

@@

Let $T \in (0, \infty)$ be given, and set $I := (0, T)$. We make the following assumption.
\begin{assum}
  \label{assum:a}
  For a.e.~$t$, let $a(t;\cdot,\cdot)$ denote a bilinear form on $V \times V$ that is
  \begin{alignat*}{3}
    t \mapsto a(t; \eta, \zeta) & ~~ \text{is measurable} \quad && (\eta, \zeta \in V), \\
    |a(t;\eta,\zeta)| & \lesssim  \|\eta\|_{V} \|\zeta\|_{V} &&(\eta,\zeta \in V) &\quad&\text{(bounded)}, \\
     a(t;\eta,\eta)   & \gtrsim   \|\eta\|_{V}^2 &&(\eta \in {V}) &&\text{(coercive)}.
  \end{alignat*}
\end{assum}

@@

\subsection{Andreev formulation}
Defining $A, A_s \in \Lis(Y,Y')$, $A_a \in \cL(Y,Y')$, and $\partial_t \in \cL(X,Y')$ by 
\[
(Au)(v):=\int_I a(t;u(t),v(t)) \dif t, \quad A_s:=\tfrac12(A+A'), \quad A_a:=\tfrac12(A-A'), \quad \partial_t:=B-A,
\]
an equivalent self-adjoint saddle point formulation of \eqref{eqn:B-varform} was
introduced by Andreev in \cite{Andreev2013} as finding the solution $(\mu,u) \in Y\times X$ of
\[
  \begin{bmatrix} A_s & B\\ B' & -\gamma_0' \gamma_0 \end{bmatrix}
  \begin{bmatrix} \mu \\ u \end{bmatrix}=
  \begin{bmatrix} g \\ -\gamma_0' u_0 \end{bmatrix}.
\]
Thanks to \eqref{eqn:B-lis}, the Schur complement operator $S := B' A_s^{-1} B+\gamma_0'\gamma_0$ is self-adjoint, coercive, and in $\Lis(X, X')$.

@@

Let $(X^\delta)_{\delta \in \Delta}$ be a collection of closed subspaces of $X$. 
We define a \emph{partial order} on $\Delta$ by $\delta \preceq \tilde{\delta}$
when $X^\delta \subseteq X^{\tilde{\delta}}$. For $\delta \in \Delta$, let
$u_\delta \in X^\delta$ denote the {\em Galerkin approximation to $u$}, i.e., the solution of
\begin{equation}
(Su_\delta)(v)=f(v) \quad (v \in X^\delta), 
  \label{eqn:galerkin}
\end{equation}
being the best approximation to $u$ from $X^\delta$ wrt.~$\|\cdot\|_X$.

\subsection{Discretized problem}
Applying $S$ requires the application of the nonlocal operator $A_s^{-1}$, making it
unsuitable for practical computation. To that end, let $(Y^\delta)_{\delta \in \Delta}$
be a collection of closed subspaces of $Y$ satisfying $X^\delta \subseteq Y^\delta$
that is \emph{uniformly inf-sup stable}, i.e.
\begin{equation}
  \gamma_\Delta:=\inf_{\delta \in \Delta}\inf_{0 \neq w \in X^\delta}\sup_{0\neq v \in Y^\delta} \frac{(\partial_t w)(v)}{\|\partial_t w\|_{Y'}\|v\|_Y} \in (0,1].
  \label{eqn:infinfsup}
\end{equation}
Uniform stability essentially establishes the norm equivalences
\[
  \gamma_\Delta \|\partial_t w\|_{Y'} \leq \|\partial_t w\|_{{Y^\delta}'} \leq \|\partial_t w\|_{Y'} \quad (w \in Y, \delta \in \Delta).
\]
Note that $\gamma_\Delta$ can be made arbitrarily close to $1$ by selecting $Y^\delta$ sufficiently large.

For $\delta, \hat{\delta} \in \Delta$ with $Y^\delta \subseteq Y^{\hat{\delta}}$, and 
$E_Y^{\hat{\delta}}$, $E_X^\delta$ denoting the embeddings $Y^{\hat{\delta}} \rightarrow Y$,
$X^\delta \rightarrow X$, let $(\mu^{\hat{\delta} \delta},u^{\hat{\delta} \delta}) \in Y^{\hat{\delta}} \times X^\delta$ be the solution of 
\[
  \begin{bmatrix}{E_Y^{\hat{\delta}}}' A_s E_Y^{\hat{\delta}}& {E_Y^{\hat{\delta}}}' B E^\delta_X\\ {E^\delta_X}' B' E_Y^{\hat{\delta}}& -{E^\delta_X}' \gamma_0' \gamma_0 E^\delta_X \end{bmatrix}
  \begin{bmatrix} \mu^{\hat{\delta} \delta} \\ u^{\hat{\delta} \delta} \end{bmatrix}
  \begin{bmatrix} {E^{\hat{\delta}}_Y}' g \\ -{E^\delta_X}' \gamma_0' u_0 \end{bmatrix}
\]
or
\begin{equation}
  \label{eqn:discr-schur}
  \underbrace{
    {E^\delta_X}'(B' E^{\hat{\delta}}_Y({E^{\hat{\delta}}_Y}' A_s E^{\hat{\delta}}_Y)^{-1} {E^{\hat{\delta}}_Y}' B +\gamma_0'\gamma_0)E^\delta_X
  }_{S^{\hat{\delta} \delta}:=}u^{\hat{\delta} \delta}
  =
  \underbrace{
    {E^\delta_X}' (B' E^{\hat{\delta}}_Y({E^{\hat{\delta}}_Y}' A_s E^{\hat{\delta}}_Y)^{-1} {E^{\hat{\delta}}_Y}' g+\gamma_0' u_0)
  }_{f^{\hat{\delta} \delta}:=}.
\end{equation}\rvv{heavy notatie uitstellen?}
Unless $Y^{\hat{\delta}}=Y$, it holds that $S^{\hat{\delta} \delta} \neq {E_X^\delta}' S E_X^\delta$ and $f^{\hat{\delta} \delta} \neq {E_X^\delta}'f$, and so generally $u^{\hat{\delta} \delta} \neq u_\delta$.

Equipping $X^\delta$ with `energy' norm $\|w\|^2_{X^{\hat{\delta}\delta}}:=\|w\|^2_{Y}+ \|\partial_t w\|_{{Y^\delta}'}+\|\gamma_T w\|^2$,
from \cite[Lemma~3.4]{Stevenson2020a} it follows that
$\|\cdot\|_{X^{\hat{\delta}\delta}}^2=(S^{\hat{\delta}\delta}\cdot)(\cdot)$,
similar to Lemma~\ref{lem:energy-norm}. As shown in \cite[Thm.~3.7]{Stevenson2020a}, we have
\begin{equation}
  \label{eqn:galerkin-ortho}
  \|u-u^{\hat{\delta}\delta}\|_X \leq \gamma_\Delta^{-1} \|u-u_\delta\|_X,
\end{equation}
whereas by definition of $\gamma_\Delta$ it holds that
\begin{equation}
  \label{eqn:X-norm-equiv}
  \gamma_\Delta\|\cdot\|_{X} \leq \|\cdot\|_{X^{\hat{\delta}\delta}} \leq \|\cdot\|_{X} \quad\text{on } X^\delta.
\end{equation}

@@

We will instead build our spaces as linear combinations ofwavelets in time with
finite elements in space, thus preserving some of the usual methodology for solving
PDEs numerically.

\subsection{The spatial meshes}
The following result generalizes~\cite[Lemma 6.2]{Andreev2013}
and~\cite[Proposition 2.5]{Tantardini2016} by allowing $W \neq \tilde W$.

@@

\subsection{Wavelets in time, finite elements in space}
\jw{Willen we hier $\tilde Y^\delta$ houden ookal is hij gewoon $=Y^\delta$?}
Let ${\mathcal O}$ be a collection of pairs of closed subspaces $(W,\tilde{W})$
as in Proposition~\ref{prop:space-infsup} with uniform inf-sup constant $\gamma>0$.

@@

We will assume that $\Sigma$ and $\Psi$ are locally supported, which in particular
means that $|\supp \sigma_\lambda| \lesssim 2^{-|\lambda|}$ and
$|\supp \psi_\lambda| \lesssim 2^{-|\lambda|}$. Furthermore, to ensure an
efficient stiffness matrix evaluation, we will shortly impose a \emph{doubletree constraint}\jw{definitie maken?}
on $X^\delta$ and $Y^\delta$, which will have the consequence that for any
$\lambda \in \vee_\Sigma$ with $\tilde{W}_\lambda^\delta \neq \{0\}$, and any
$\ell <|\lambda|$, there exists a $\mu \in \vee_\Sigma$ with $|\mu|=\ell$
($\mu$ being the `ancestor' of $\lambda$) with
$\dist(\supp \sigma_\mu,\supp \sigma_\lambda)\lesssim 2^{-|\mu|}$ and
$\tilde{W}_\mu^\delta \supset \tilde{W}_\lambda^\delta$.
We infer that \eqref{eqn:Y-space-refined} and thus \eqref{eqn:pre-doubletree} can
be ensured for $Y^\delta$ with $\dim Y^\delta \lesssim \dim X^\delta$.

In particular, under the doubletree constraint on $X^\delta$, \eqref{eqn:Y-space-refined}
is ensured under the condition that\jw{ik heb dit niet gecheckt, bovendien heb ik $S(\lambda)$ eruit gesloopt}
\[
  |\mu| = |\lambda| \wedge|\supp \psi_\mu \cap \supp \sigma_\lambda|>0 \implies \tilde{V}^\delta_\mu \supset  \tilde{W}^\delta_\lambda \quad (\lambda \in \vee_\Psi).
\]
\jw{Dit is min-of-meer copy-paste uit followup maar ik vind het nu nog wel cryptisch :-(}

\begin{example}
  Consider pairs $(W, \tilde W) \in \mathcal O$ where $W = \tilde W$.
  Let any $\sigma_\lambda$ be a continuous piecewise polynomial of degree $d-1$\jw{voor $d$ de dimensie van je space domain?! of gewoon *een* $d$? in het tweede geval: rename naar $p$?}
  wrt.~a uniform partition of $I$ into $2^{|\lambda|}$ subintervals, and let 
  $\Psi=\tilde{\Psi}$ be such that $\spann\{\tilde{\psi}_\lambda : |\mu| \leq |\lambda|\}$
  includes all piecewise polynomials of degree $d-2$ wrt.~a uniform partition
  of $I$ into $2^{|\lambda|}$ subintervals so that \eqref{eqn:deriv-orthogonal}
  is satisfied. If $\spann\{\tilde{\psi}_\lambda : |\mu| \leq |\lambda|\}$ even
  includes all piecewise polynomials of degree $d-1$ wrt.~a uniform partition
  of $I$ into $2^{|\lambda|}$ subintervals, then $Y^\delta$ as constructed above
  additionally satisfies
  \begin{equation}
    \label{eqn:inclusion}
      \framebox{$X^\delta \subset Y^\delta$}.
  \end{equation}
\end{example}

\subsubsection{Our choice of wavelets}
\label{sec:wavelets}
In the temporal axis, we consider piecewise linear wavelets. For $\Sigma$, we take the continuous three-point from \cite{Stevenson1998}; cf.~Figure~\ref{fig:3pt-wavelet}.
\begin{figure}
  \caption{TODO: Three-point wavelet.}
  \label{fig:3pt-wavelet}
\end{figure}

For $\Psi$, we take the discontinuous orthogonal piecewise linear wavelet basis
of Figure~\ref{fig:ortho-wavelet}\jw{again, needs citation; ik kon niks vinden zo 1-2-3;
misschien omdat het niet echt een ``wavelet'' in de typische zin is?}
\begin{figure}
  \caption{orthogonal wavelet.}
  \label{fig:ortho-wavelet}
\end{figure}

In the spatial axis, we consider the collection $\mathbb T$ of conforming
triangulations generated by NVB from some coarsest triangulation $\T_\perp$,
and define $V_\T = \tilde V_\T$ the space of continuous piecewise linears wrt.~$\T$
that vanish on $\partial \Omega$ such that $X^\delta := \sum_{\lambda \in \vee^\delta_\Sigma} \sigma_\lambda \otimes V_{\T_{\vee^\delta_\Sigma, \lambda}}$ satisfies the doubletree constraint.
This means that when $\mu \in \vee^\delta_\Sigma$ is a parent of $\lambda \in \vee^\delta_\Sigma$,
    then $\T_{\vee^\delta_\Sigma, \mu}$ is a refinement of $\T_{\vee^\delta_\Sigma, \lambda}$, and that $\vee^\delta_\Sigma$ is a subtree of $\vee_\Sigma$, meaning
\begin{itemize}
  \item it contains all wavelets on level 0, and
  \item if it contains a wavelet of level $\lambda \geq 1$, then it also contains
    its parents.
\end{itemize}

\begin{remark}
  When equipping the finite element spaces $V_{\T}$ with the hierarchical basis,
  this doubletree constraint coincides with the multi-index constraint on the index
  set of the basis for $X^\delta$; see e.g.~\cite{TODO}.
\end{remark}

We consider spaces $Y^\delta = \tilde Y^\delta$ of the form
$Y^\delta := \sum_{\lambda \in \vee^\delta_\Psi} \psi_\lambda \otimes V_{\T_{\vee^\delta_\Psi, \lambda}}$
for $\T_{\vee^\delta_\Psi, \lambda} \in \mathbb T$, again satisfying the doubletree
constraint. The choice
\begin{equation}
  Y^\delta = \sum_{\lambda \in \vee_\Sigma^\delta} \sum_{\{\mu \in \vee_\Psi\colon |\mu|=|\lambda|,\,
  |\supp \sigma_\lambda \cap \supp \psi_\mu|>0\}} \psi_\mu \otimes V_{\T_{\vee_\Sigma^\delta,\lambda}}
  \label{eqn:generate-Ydelta}
\end{equation}
is a doubletree by virtue of $X^\delta$ being one, and for this pair $(X^\delta, Y^\delta)$,
\eqref{eqn:d_tX-in-Y} and \eqref{eqn:inclusion} are valid.
